MCTS Applied to Co-operative Problems

### 2015-07-02 Report/ceec.tex
Fixed MCTS

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}

\begin{document}
\maketitle
\begin{abstract}
An experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through. Two agents have to each reach every goal present on the map. For a door to be open, an Agent must be present on at least one of the buttons that is linked to it.

@@

\section{Introduction}
Place decent literature review here covering:
\begin{itemize}
\item{Basic \gls{mcts}}
\item{Basic MAS}
\item{The problem itself}
\end{itemize}

\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}. Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.

Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently. \gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward.

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Walls - } Walls are impassable, and are fixed in position. Rendered in Black.}
\item{\emph{Agents - } Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors - } Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
\item{\emph{Buttons - } Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals - } Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect}
\end{itemize}

@@

\subsection{Methodology}
Initially, observations were made to see how \gls{mcts} handled the problem. At first, with a short computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.

@@

With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better. Typical behaviour would be near optimal with significantly less random sections of movement. This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.

>>>>

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}
\newacronym{mas}{MAS}{Multi-Agent Systems}

\begin{document}
\maketitle
\begin{abstract}
This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through. Two agents have to each reach every goal present on the map. For a door to be open, an Agent must be present on at least one of the buttons that is linked to it.

@@

\section{Introduction}

\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}. Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.

Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently. \gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children.

Traditional \gls{mas} would be the logical choice for solving this type of problem, however they were left out in order to work towards a co-operative \gls{ggp} agent.

Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players. 
\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Doors} are rendered in Black.}
\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect. \emph{Goals} are rendered in Yellow}
\end{itemize}

@@

\subsection{Methodology}
Initially, observations were made to see how \gls{mcts} handled the problem. At first, with a small computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.

@@

With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better. Typical behaviour would be near optimal with significantly less random sections of movement. This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
\bibliographystyle{IEEEtran}
\bibliography{ceec}
